---
title: "Female Cancer incidences in Coimbatore"
resource_files:
- finalpointmerge.dbf
- finalpointmerge.sbn
- finalpointmerge.shx
- finalpointmerge.sbx
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(rgdal)
library(shiny)
library(leaflet)
library(highcharter)
library(maptools)
library(htmltools)
data<-readShapePoints("finalpointmerge.shp") 
data1<-data.frame(data)
xy = data1[c("coords.x1", "coords.x2")] # retrieve coordinates as data.frame
class(data1)
coordinates(data1) = c("coords.x1", "coords.x2")
coordinates(data1)
class(data1)
```

Column {data-width=400}
-----------------------------------------------------------------------
### Background
This interactive map shows the individual locations of the female cancer incidences in the study area.


The interactive atlas makes use of the following R packages

1. `flexdashboard`: https://cran.r-project.org/web/packages/flexdashboard/index.html
2. `leaflet`: https://cran.r-project.org/web/packages/leaflet/index.html
3. `highcharter`: https://cran.r-project.org/web/packages/highcharter/index.html
4. `maptools`: https://cran.r-project.org/web/packages/maptools/index.html
5. `shiny`: https://cran.r-project.org/web/packages/shiny/index.html

The user can click any circle marker and the corresponding interactive bargraph will be displayed showing the cancer burden in that particular region


The atlas could be used by health professionals and researchers to come up with better prevention and control strategies in the specific subpopulations


Column {data-width=600}
-----------------------------------------------------------------------
### Interactive map
```{r}
output$Map <- renderLeaflet({
    leaflet(data1) %>% addTiles() %>% addCircleMarkers(data = data1, lng = data1$coords.x1 , lat = data1$coords.x2,color="red",stroke=F,fillOpacity=0.5,
               layerId = ~ID, popup = ~htmlEscape(POINT), radius=~(data1$TOTAL/5)) 

  })

observeEvent(input$Map_marker_click, {
    p <- input$Map_marker_click
	if(p$id=="Selected"){
		leafletProxy("Map") %>% removeMarker(layerId="Selected")
	} else {
		leafletProxy("Map") %>% setView(lng=p$lng, lat=p$lat, input$Map_zoom) %>% addCircleMarkers(p$lng, p$lat, radius=10, color="black", fillColor="orange", fillOpacity=1, opacity=1, stroke=TRUE, layerId="Selected")
	}
})

leafletOutput('Map')  

```

### Interactive Graph

```{r}

click_marker <- eventReactive(input$Map_marker_click, {

  x <- input$Map_marker_click

  return(x$id)


})

data_for_chart <- reactive({

  return(data1[data1$ID == click_marker(), ])

})

output$chart <- renderHighchart({

  highchart() %>%
 hc_add_theme(hc_theme_ft())%>%
  hc_chart(type = 'column') %>%
  hc_xAxis(categories=list(data_for_chart()$POINT))%>%
  hc_add_series(name="breast",data=data_for_chart()$BREASTF,color="red")%>%
  hc_add_series(name="gastro",data=data_for_chart()$GASTROF, color="blue")%>%
  hc_add_series(name="gyaeno",data=data_for_chart()$GYNECF,color="violet")%>%
hc_add_series(name="head&neck",data=data_for_chart()$HEADNECF,color="yellow")%>%
hc_add_series(name="respiratory",data=data_for_chart()$RESPIROF,color="green")
})

highchartOutput('chart')
options(shiny.sanitize.errors = TRUE)