---
title: "Female Cancer incidences in Coimbatore"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(rgdal)
library(shiny)
library(leaflet)
library(highcharter)
library(maptools)
library(htmltools)
data<-readShapePoints("finalpointmerge.shp") 
data1<-data.frame(data)
xy = data1[c("coords.x1", "coords.x2")] # retrieve coordinates as data.frame
class(data1)
coordinates(data1) = c("coords.x1", "coords.x2")
coordinates(data1)
class(data1)
```

Column {data-width=400}
-----------------------------------------------------------------------
### chart 1
This interactive map shows the individual locations of the female cancer incidences in the study area 

Column {data-width=600}
-----------------------------------------------------------------------
### chart 2
```{r}
output$Map <- renderLeaflet({
    leaflet(data1) %>% addTiles() %>% addCircleMarkers(data = data1, lng = data1$coords.x1 , lat = data1$coords.x2,color="red",stroke=F,fillOpacity=0.5,
               layerId = ~ID, popup = ~htmlEscape(POINT), radius=~(data1$TOTAL/5)) 

  })

observeEvent(input$Map_marker_click, {
    p <- input$Map_marker_click
	if(p$id=="Selected"){
		leafletProxy("Map") %>% removeMarker(layerId="Selected")
	} else {
		leafletProxy("Map") %>% setView(lng=p$lng, lat=p$lat, input$Map_zoom) %>% addCircleMarkers(p$lng, p$lat, radius=10, color="black", fillColor="orange", fillOpacity=1, opacity=1, stroke=TRUE, layerId="Selected")
	}
})

leafletOutput('Map')  

```

### chart 3

```{r}

click_marker <- eventReactive(input$Map_marker_click, {

  x <- input$Map_marker_click

  return(x$id)


})

data_for_chart <- reactive({

  return(data1[data1$ID == click_marker(), ])

})

output$chart <- renderHighchart({

  highchart() %>%
 hc_add_theme(hc_theme_ft())%>%
  hc_chart(type = 'column') %>%
  hc_xAxis(categories=list(data_for_chart()$POINT))%>%
  hc_add_series(name="breast",data=data_for_chart()$BREASTF,color="red")%>%
  hc_add_series(name="gastro",data=data_for_chart()$GASTROF, color="blue")%>%
  hc_add_series(name="gyaeno",data=data_for_chart()$GYNECF,color="violet")%>%
hc_add_series(name="head&neck",data=data_for_chart()$HEADNECF,color="yellow")%>%
hc_add_series(name="respiratory",data=data_for_chart()$RESPIROF,color="green")
})

highchartOutput('chart')
options(shiny.sanitize.errors = TRUE)